---
title: "Project 1"
author: "Tony Nguyen"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    csl: biomed-central.csl
    df_print: paged
    fig_caption: yes
    fig_height: 6
    fig_width: 7
    number_sections: yes
    theme: journal
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    df_print: kable
    fig_caption: yes
    fig_height: 6
    fig_width: 7
    highlight: tango
    toc: yes
    toc_depth: 4
#bibliography: project.bib
abstract: This project is all about analysing the SWDEFECTS file using R and probability theory. Here we are investigating data from the software defects file, SWDEFECTS.csv. We start by summarizing the data and then making a formula of how to calculate efficiency in catching defects. We then make a bar graph of the defects found. Afterwards we test the Accuracy, Detection Rate, False Alarm Rate, and Precision of capturing these defects. We then make a bar graph to better visual the process.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction to the data

## Data and variables(see MS pg. 77,125)
Describe the data and the problem we wish to investigate.

## Summary Table 

Creating the summary table (TABLE SIA3.2) found on page 125 in MS book.

```{r}
summary <- matrix(c("", "No", "Yes", "", "False", "a", "c", "", "True", "b", "d", ""), ncol = 3)

colnames(summary) <- c("", "Module", "Has Defects")
rownames(summary) <- c("", "Algorithm", "Predicts", "Defects")
summary.table <- as.table(summary)
summary.table
```


Using $\LaTeX$ construct the formulae for 

1. Accuracy
2. Detection rate
3. False alarm rate
4. Precision

Latex Example: See (http://www.stat.cmu.edu/~cshalizi/rmarkdown/#elements-of-math-mode)

$$
\begin{eqnarray}
P(|X-\mu| > k) & = & P(|X-\mu|^2 > k^2)\\
& \leq & \frac{\mathbb{E}\left[|X-\mu|^2\right]}{k^2}\\
& \leq & \frac{\mathrm{Var}[X]}{k^2}
\end{eqnarray}
$$

# R functions
Using the above definitions make R functions that will create the required probabilities:

```{r accuracy, eval=TRUE}
acc=function(a,b,c,d)
{
  (a + d)/(a + b + c + d)
}
```

```{r detecton, eval=TRUE}
detect=function(b,d)
{
  (d)/(b + d)
}
```

```{r alarm, eval=TRUE}
falarm=function(a,c)
{
  (c)/(a + c)
}
```

```{r precision, eval=TRUE}
prec=function(c,d)
{
  (d)/(c + d)
}
```


# Create the tables in Figure SIA3.1
Making the software defect table and a bar graph of it.
```{r}
softwareDefect <- matrix(c("LOC > 50", "v(g) > 10)", "ev(g) >= 14.5", "iv(g) >= 9.2", "LOC = lines of code", "v(g) = number of linearly independent paths", "ev(g) = number of subflow graphs with D-structured primes", "iv(g) = cyclomatic complexity of module's reduced flow graph"), ncol = 2)

colnames(softwareDefect) <- c("Deflects Algorithm", "Definitions")

rownames(softwareDefect) <- c("Lines of code", "Cyclomatic complexity", "Essential complexity", "Design complexity")

softwareDefect.table <- as.table(softwareDefect)
softwareDefect.table

swd = read.csv("SWDEFECTS.csv")
head(swd)
tab1 = with(swd, table(c(predict.loc.50, predict.vg.10, predict.evg.14.5, predict.ivg.9.2, defect)))
barplot(tab1, beside=TRUE, leg=TRUE)
tab2 = addmargins(tab1)
tab2
```



# TABLE SIA3.3 on page 127 in the MS Statistics book.

Below we will create table SIA3.3 using the mybar() function. We will call the table tab3.

>
    1. tab ( this will be a n by m table) - like `tab3`
    2. acc ( accuracy of the decimal output ) -- like `acc=4` for example

SIA3.3 Table    
```{r}
tab3 <- matrix(c(0.843, 0.825, 0.990, 0.869, 0.408, 0.286, 0.041, 0.224, 0.091, 0.116, 0.018, 0.060, 0.333, 0.212, 0.200, 0.289), ncol=4)

colnames(tab3) <- c('Accuracy', 'Detection Rate', 'False Alarm Rate', 'Precision')
rownames(tab3) <- c("Lines of code", "Cyclomatic complexity", "Essential complexity", "Design complexity")

tab3.table <- as.table(tab3)
tab3.table
```

The function will need to create two things

>
    1. A barplot of the table
    2. Commandline output in the form of a list containing the table

mybar function
```{r}
mybar=function(tab, acc)
{
  barplot(round(tab, acc), col = rainbow(acc), legend = rownames(tab), beside = TRUE)
}

mybar(tab = tab3, acc = 4)
```

